Exploring Conformational Dynamics and Related Time Scales via Nonequilibrium Molecular Dynamics Simulation

### 2013-08-20 writedown/npt-neq/alanine.tex
revise, send the source to Luigi

In this section,
we want to study the nonequilibrium properties of an alanine dipeptide
under a constant EF.  At time $t=0$~ps, the system
has been fully equilibriated without any EF. From $t=0$ to
$t=t_{\textrm{init}}$, the eclectic field is switched on linearly, while
after $t=t_{\textrm{init}}$, the field is kept constant at
$E_{\infty}$.  In this work we consider $t_{\textrm{init}} = 10$~ps,
and $E_{\infty} = 1$~V/nm.
The direction of this field is arbitrarily chosen: along the
$x$ direction. Since the dipole of the equilibrium configurations of
alanine can be along any direction, applying the electric along $x$-axis is
not biased.
Being more general, in this paper we denote the
EF as a function of time $\vect E(t)$.
Therefore, the constant EF is
$\vect E(t) = (E_\infty\cdot t/t_{init},0,0)$ as $0\leq t < t_{init}$, and 
$\vect E(t) = (E_\infty,0,0)$
as $t \geq t_{init}$.
The system is set up in a $2.7\times 2.7\times
2.7\, \textsf{nm}^3$ periodic simulation region, with one alanine dipeptide
described by the CHARMM27 force field, and solved in 644 TIP3P
water molecules.
The EF exserts force $\vect F = q \vect E(t)$ on
the partial charge $q$ in the system.
The size of the  Hamiltonian dynamics region is $R_{ex} = 1.0$~nm.
All simulations are performed by a home-modified GROMACS 4.5~\cite{pronk2013gromacs}.
Firstly, an equilibrium NVT simulation of
100~\textsf{ns} was performed with a Langevin thermostat (time-scale
$\tau_T = 0.5~\textsf{ps}$) coupled to the system for constant
temperature.  Along the trajectory, configurations were taken every
50~\textsf{ps}, so we use 2000 initial configurations for each nonequilibrium
MD simulation, if not stated otherwise.
% They server as starting point of the branching
% trajectories.
The branching trajectories were integrated by the
Leap-frog scheme with the aforementioned nonequilibrium
temperature control technique.  The
time step was $\Delta t = 0.002~\textsf{ps}$. The short-range
interaction was smoothed from $0.8$ to $1.0~\textsf{nm}$ by the
``switch'' method provided by Gromacs.  An energy conserving PME
method was applied to calculate the electrostatic interaction in this
periodic system. In the thermostating region, the original dynamics was
coupled to a Langevin thermostat with $\tau_T = 0.1~\textsf{ps}$.
The whole system is also coupled to a Parrinello-Rahman barostat with $\tau_P = 2.0~\textsf{ps}$ to keep
the pressure at the ambient condition (1~Bar). Since the
change of the system size is small and slow, the pressure control
does not have an obviously effect on the
dynamics of the system.

@@

On each branching trajectory, to easy the analysis of the conformation
of alanine dipeptide, the molecular configuration is projected on
the Ramachandran histogram, as
shown in Fig.~\ref{fig:tmp4}. The equilibrium distribution of the
conformation is given in the left plot, and the fully relaxed
conformation under $E_{\infty} = 1$~V/nm is given in the right plot.  It is
clear the conformations are populated in several clusters, and the
position of the clusters do not change when the external electric
field is applied.
This means that only a few of the conformations are likely to be observed,
while there is nearly no opportunity to see others. 
These conformations are called ``metastable states''.
The strict definition of the
metastability is not exactly the same as those conformations that are likely to be observed.
Since in this paper we do not focus on the discussion of the definition for the metastability of the system,
we assume they have the same meaning.
We manually divide the
Ramachandran histogram into 5 subregions, see Fig.~\ref{fig:tmp4},
then the observation on the Ramachandran histogram is projected to the
observation of these 5 states, i.e. $\{A_1, A_2, B_1, B_2, C\}$, which
correspond to the molecular conformations we are investigating in this work.
These subregions
correspond to different secondary structure of a peptide chain:
$A_1$ and $A_2$ are
corresponding to the alpha helix. $B_1$ and $B_2$ are
corresponding to the beta sheet. $C$ is corresponding to the
left-handed alpha helix.

From Fig.~\ref{fig:tmp4}, it is obvious that the population in each
metastable state changes due to the external EF, for
example, the population of state $C$ vanishes in equilibrium,
but plays an important role when the EF is applied. We
therefore want to study how the alanine changes from one conformation
to the other, how fast is the change, and the relations to the 
the EF. 
Firstly, we calculate the probability of being in a certain state that
is defined by:
\begin{align}
  P_I(t) = \mathbb P (\vect x_t \in I), \quad  I \in \{A_1, A_2, B_1, B_2, C\},
\end{align}
please notice that the time dependency of the probability, so it is
a nonequilibrium observable.
% which is the time dependent probability of the alanine being in metastable
% state $I$.
% Secondly, we study the
% forward and backward transition probability of the metastable conformations, which is defined by
% \begin{align}
%   P^{\fwd}_{J,I}(t) & = \mathbb P( \vect x_{t+\Delta t} \in J | \vect x_t \in I) \\
%   P^{\bwd}_{J,I}(t) & = \mathbb P( \vect x_{t-\Delta t} \in J | \vect x_t \in I) 
%   % \qquad I, J \in \{A_1, A_2, B_1, B_2, C\},
% \end{align}
% where $\Delta t$ is the time-scale of the observation.
% For a revserible and homogeneous Markov process, it is easy to show
% that $P^{\fwd}_{J,I} = P^{\bwd}_{J,I}$, and both of them are time independent. For a general nonequilibrium
% process considered by the present work, this relation is genarlly not guarenteed.
Secondly,
we study the net probability flux from metastable state $I$ to $J$, defined by:
\begin{align}\nonumber
  F_{J,I}(t) & =\lim_{\Delta t\rightarrow 0} \frac1{\Delta t} [\mathbb P( \vect x_{t-\Delta t} \in J, \vect x_t \in I) - \mathbb P( \vect x_{t-\Delta t} \in I, \vect x_t \in J)], \\\label{eqn:tmp7}
  & J,I \in \{A_1, A_2, B_1, B_2, C\}.
\end{align}
which presents the rate of how much conformation $J$ is changed
into $I$. A positive value indicates the
net flux from $J$ to $I$,
while a negative value indicates a net flux from $I$ to $J$.
Now project the original nonequilibrium process $\vect x_t$
onto the discretized states $\{A_1, A_2, B_1, B_2, C\}$,
if the resulting reduced process 
is time-reversible, then it is obvious that
$ F_{J,I}(t) = 0$. In an other word, the quantity $ F_{J,I}(t) $ represents
the irreversibility of the reduced process on
$\{A_1, A_2, B_1, B_2, C\}$.
In practice, to measure $ F_{J,I}(t)$, one need firstly approximate the limit
in Eq.~\eqref{eqn:tmp7} by the finite difference,
then calculate the joint probabilities on
the right-hand-side from the molecular trajectories.
If one wants a precise finite difference approximation, a smaller $\Delta t$ is
preferable,
but then the statistical uncertainty of measuring the joint probabilities
is higher. In practice,
we use a $\Delta t$ that is small enough for a precise finite difference approximation,
and not too small so that the joint probabilities can be calculated properly.
In the oscillating EF case, the net probability flux is also highly oscillating,
so it is convenient to study the integrated probability flux:
\begin{align}
  Q_{J,I} (t) = \int_0^t F_{J,I}(\tau)d \tau,
\end{align}
which presents the time averaged effect of the EF to the molecular conformation.

@@

\begin{figure}
  \centering
  \includegraphics[]{fig.ala/fig-meta-npt.eps}
  \caption{The probability of being in a metastable states under a constant EF.
    The warm-up time $t_{init} = 10$~ps. The red line stands for state $A_1$,
    green for $A_2$, dark blue for $B_1$, purple for $B_2$ and light blue
    for $C$.
  }
  \label{fig:tmp5}
\end{figure}

\begin{figure}
  \centering
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-1.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-2.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-3.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-4.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-5.eps}\\
  % \caption{The populations of the metastable sets as a function of time.
  %   The dashed vertical lines indicate the three different time scale of
  % metastable set population at $t_{\textrm{init}} = 10~\textsf{ps}$.}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-1.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-2.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-3.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-4.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-5.eps}\\
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-flux-1.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-flux-2.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-flux-3.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-flux-4.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-flux-5.eps}\\
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-iflux-1.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-iflux-2.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-iflux-3.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-iflux-4.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-iflux-5.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-iflux-1.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-iflux-2.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-iflux-3.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-iflux-4.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-iflux-5.eps}\\
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-500-iflux-1.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-500-iflux-2.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-500-iflux-3.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-500-iflux-4.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-500-iflux-5.eps}
  \caption{
    The net probability flux and its integration under the constant EF case.
    The warm-up time $t_{init} = 10$~ps.
    The first row shows the probability flux $F_{J,I}(t)$ with unit $\textrm{ps}^{-1}$, while the second
    shows the integrated  probability flux denoted by $Q_{J,I}(t)$.
    A constant $Q_{J,I}$ means vanishing net flux, while a increasing (deceasing)
    $Q_{J,I}$ indicates positive (negative) net flux.
    From left to right, the five
    columns present $I = A_1$, $A_2$, $B_1$, $B_2$ and
    $C$, respectively. In each plot, the red line stands for $J=A_1$,
    green for $J=A_2$, dark blue for $J=B_1$, purple for $J=B_2$ and light blue
    for $J=C$. 
    }
  \label{fig:tmp6}
\end{figure}

% \begin{figure}
%   \centering
%   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-fwd-1.eps}
%   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-fwd-2.eps}
%   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-fwd-3.eps}
%   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-fwd-4.eps}
%   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-fwd-5.eps}\\
%   % \caption{The populations of the metastable sets as a function of time.
%   %   The dashed vertical lines indicate the three different time scale of
%   % metastable set population at $t_{\textrm{init}} = 10~\textsf{ps}$.}
%   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-bwd-1.eps}
%   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-bwd-2.eps}
%   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-bwd-3.eps}
%   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-bwd-4.eps}
%   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-bwd-5.eps}\\
%   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-flux-1.eps}
%   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-flux-2.eps}
%   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-flux-3.eps}
%   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-flux-4.eps}
%   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-flux-5.eps}
%   \caption{Forward and backward nonequilibrium transition probability of the case $t_{init} = 10$~ps.}
%   \label{fig:tmp6}
% \end{figure}

The time-dependent probability of the system in a certain metastable state is given in
Fig.~\ref{fig:tmp5}. The beta sheet conformation,
which presents at the beginning,
fades away as the system relaxes to the new equilibrium. The
probability of alpha helix $A_1$ conformation grows from 45\% to 70\%.
Alpha helix $A_2$  does not change a lot under the EF.
The left-hand helix configuration $C$ noticeably grows from 0\% to 20\%.

We plot the net probability fluxes and their integration in Fig.~\ref{fig:tmp6}.
When $t$ is short, the net fluxes are generally non-zero.
When $t$ goes to infinity,
all fluxes converge to zero. This indicates
when the EF is switched on, the system firstly is driven from the old
equilibrium (in zero EF), and this is a nonequilibrium process.
After a long enough time, the system
is fully relaxed to the new equilibrium defined by the constant EF,
% it gradually relaxes to the new equilibrium,
so we do not see and change
in the population of the metastable states.

\begin{table}
  \centering
  \begin{tabular*}{0.4\textwidth}{@{\extracolsep{\fill}}lc}\hline\hline
    Direction        & time scale [ ps ] \\\hline
    $A_1\rightarrow A_2$        &       $0\sim 10$      \\
    $B_1\rightarrow B_2$        &       $0\sim 10$      \\    
    $A_2\rightarrow A_1$        &       $10\sim 100$      \\
    $B_2\rightarrow B_1$        &       $10\sim 100$      \\    
    $B_2\rightarrow A_1,\ A_2,\ C$        &       $10\sim 50$      \\    
    $B_1\rightarrow A_1,\ C$        &       $10\sim 500$      \\    \hline\hline
  \end{tabular*}
  \caption{A list of main probabilty fluxes and the corresponding time scales observed in the constant EF case.}
  \label{tab:tmp1}
\end{table}

>>>>

In this section,
we want to study the nonequilibrium properties of an alanine dipeptide
under a constant EF.  At time $t=0$~ps, the system
has been fully equilibriated without any EF. From $t=0$ to
warm-up time $t=t_{\textrm{warm}}$, the eclectic field is switched on linearly, while
after $t=t_{\textrm{warm}}$, the field is kept constant at
$E_{\infty}$.  In this work we consider $t_{\textrm{warm}} = 10$~ps,
and $E_{\infty} = 1$~V/nm.
The direction of this field is arbitrarily chosen: along the
$x$ direction. Since the dipole of the equilibrium configurations of
alanine can be along any direction, applying the electric along $x$-axis is
not biased.
Being more general, in this paper we denote the
EF as a function of time $\vect E(t)$.
Therefore, the constant EF is
$\vect E(t) = (E_\infty\cdot t/t_{warm},0,0)$ as $0\leq t < t_{warm}$, and 
$\vect E(t) = (E_\infty,0,0)$
as $t \geq t_{warm}$.
The system is set up in a $2.7\times 2.7\times
2.7\, \textsf{nm}^3$ periodic simulation region, with one alanine dipeptide
described by the CHARMM27 force field, and solved in 644 TIP3P
water molecules.
The EF exserts force $\vect F = q \vect E(t)$ on
the partial charge $q$ in the system.
The size of the  Hamiltonian dynamics region is $R_{ex} = 1.0$~nm.
All simulations are performed by a home-modified GROMACS 4.5~\cite{pronk2013gromacs}.
Firstly, an equilibrium NVT simulation of
100~\textsf{ns} was performed with a Langevin thermostat (time-scale
$\tau_T = 0.5~\textsf{ps}$) coupled to the system for constant
temperature.  Along the trajectory, configurations were taken every
50~\textsf{ps}, so we use 2000 initial configurations for each nonequilibrium
MD simulation, if not stated otherwise.
% They server as starting point of the branching
% trajectories.
The branching trajectories were integrated by the
Leap-frog scheme with the aforementioned nonequilibrium
temperature control technique.  The
time step was $\Delta t = 0.002~\textsf{ps}$. The short-range
interaction was smoothed from $0.8$ to $1.0~\textsf{nm}$ by the
``switch'' method provided by Gromacs.  An energy conserving PME
method was applied to calculate the electrostatic interaction in this
periodic system. In the thermostating region, the original dynamics was
coupled to a Langevin thermostat with $\tau_T = 0.1~\textsf{ps}$.
The whole system is also coupled to a Parrinello-Rahman barostat with $\tau_P = 2.0~\textsf{ps}$ to keep
the pressure at the ambient condition (1~Bar). Since the
change of the system size is small and slow, the pressure control
does not have an obviously effect on the
dynamics of the system.

@@

On each branching trajectory, to easy the analysis of the conformational dynamics
of alanine dipeptide, the molecular configuration is projected on
the Ramachandran histogram, as
shown in Fig.~\ref{fig:tmp4}. The equilibrium distribution of the
conformation is given in the plot (a), and the fully relaxed
conformation under $E_{\infty} = 1$~V/nm is given  plot (b).  It is
clear the conformations are populated in several clusters, and the
position of the clusters do not change when the external electric
field is applied.
This means that only a few of the conformations are likely to be observed,
in the nonequilibrium process.
These conformations are called ``metastable states''.
The strict definition of the
metastability is not exactly the same as those conformations that are likely to be observed.
Since in this paper we do not focus on the discussion of the definition for the metastability of the system,
we do not distinguish the definations, and assume they have the same meaning.
We manually divide the
Ramachandran histogram into 5 subregions, see Fig.~\ref{fig:tmp4},
then the observation of conformations on the Ramachandran histogram is projected to the
observation of these 5 states, i.e. $\{A_1, A_2, B_1, B_2, C\}$.
These states
correspond to different secondary structure of a peptide chain:
$A_1$ and $A_2$ are
corresponding to the alpha helix. $B_1$ and $B_2$ are
corresponding to the beta sheet. $C$ is corresponding to the
left-handed alpha helix.

From Fig.~\ref{fig:tmp4}, it is obvious that the population in each
metastable state changes due to the external EF, for
example, the population of state $C$ vanishes in equilibrium,
but plays an important role when the EF is applied. We
therefore want to study how the alanine changes from one conformation
to the other, how fast is the change, and the relations to the 
the EF. 
Firstly, we calculate the probability of being in a certain state that
is defined by:
\begin{align}
  P_I(t) = \mathbb P (\vect x_t \in I), \quad  I \in \{A_1, A_2, B_1, B_2, C\},
\end{align}
Notice that the time dependency of the probability, so it is
a nonequilibrium observable.
% which is the time dependent probability of the alanine being in metastable
% state $I$.
% Secondly, we study the
% forward and backward transition probability of the metastable conformations, which is defined by
% \begin{align}
%   P^{\fwd}_{J,I}(t) & = \mathbb P( \vect x_{t+\Delta t} \in J | \vect x_t \in I) \\
%   P^{\bwd}_{J,I}(t) & = \mathbb P( \vect x_{t-\Delta t} \in J | \vect x_t \in I) 
%   % \qquad I, J \in \{A_1, A_2, B_1, B_2, C\},
% \end{align}
% where $\Delta t$ is the time-scale of the observation.
% For a revserible and homogeneous Markov process, it is easy to show
% that $P^{\fwd}_{J,I} = P^{\bwd}_{J,I}$, and both of them are time independent. For a general nonequilibrium
% process considered by the present work, this relation is genarlly not guarenteed.
Secondly,
we study the net probability flux from metastable state $I$ to $J$, defined by:
\begin{align}\nonumber
  F_{J,I}(t) & =\lim_{\Delta t\rightarrow 0} \frac1{\Delta t} [\mathbb P( \vect x_{t-\Delta t} \in J, \vect x_t \in I) - \mathbb P( \vect x_{t-\Delta t} \in I, \vect x_t \in J)], \\\label{eqn:tmp7}
  & J,I \in \{A_1, A_2, B_1, B_2, C\}.
\end{align}
which presents the rate of how much conformation $J$ changes
into $I$ at time $t$. A positive value indicates the
net flux from $J$ to $I$,
while a negative value indicates a net flux from $I$ to $J$.
Now the original nonequilibrium process $\vect x_t$
is projected onto the discretized states $\{A_1, A_2, B_1, B_2, C\}$,
if the resulting reduced process 
is time-reversible, then it is obvious that
$ F_{J,I}(t) = 0$. In an other word, the quantity $ F_{J,I}(t) $ represents
the irreversibility of the reduced process on
$\{A_1, A_2, B_1, B_2, C\}$.
In practice, to measure $ F_{J,I}(t)$, one need firstly approximate the limit
in Eq.~\eqref{eqn:tmp7} by the finite difference,
then calculate the joint probabilities on
the right-hand-side from the molecular trajectories.
If one wants a precise finite difference approximation, a smaller $\Delta t$ is
preferable,
but then the statistical uncertainty of measuring the joint probabilities
is higher. In practice,
we use a $\Delta t$ that is small enough for a precise finite difference approximation,
and not too small so that the joint probabilities can be calculated properly.
In the oscillating EF case, the net probability flux is also highly oscillating,
so it is convenient to study the integrated probability flux:
\begin{align}
  Q_{J,I} (t) = \int_0^t F_{J,I}(\tau)d \tau,
\end{align}
which presents the time averaged effect of the EF to the molecular conformation.

@@

\begin{figure}
  \centering
  \includegraphics[]{fig.ala/fig-meta-npt.eps}
  \caption{The probability of being in a metastable states under a constant EF.
    The warm-up time $t_{warm} = 10$~ps. The red line stands for state $A_1$,
    green for $A_2$, dark blue for $B_1$, purple for $B_2$ and light blue
    for $C$.
  }
  \label{fig:tmp5}
\end{figure}

\begin{figure}
  \centering
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-1.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-2.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-3.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-4.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-fwd-5.eps}\\
  % \caption{The populations of the metastable sets as a function of time.
  %   The dashed vertical lines indicate the three different time scale of
  % metastable set population at $t_{\textrm{warm}} = 10~\textsf{ps}$.}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-1.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-2.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-3.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-4.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-bwd-5.eps}\\
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-flux-1.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-flux-2.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-flux-3.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-flux-4.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-flux-5.eps}\\
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-iflux-1.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-iflux-2.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-iflux-3.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-iflux-4.eps}
  \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-010-iflux-5.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-iflux-1.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-iflux-2.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-iflux-3.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-iflux-4.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-iflux-5.eps}\\
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-500-iflux-1.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-500-iflux-2.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-500-iflux-3.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-500-iflux-4.eps}
  % \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-500-iflux-5.eps}
  \caption{
    The net probability flux and its integration under the constant EF case.
    The warm-up time $t_{warm} = 10$~ps.
    The first row shows the probability flux $F_{J,I}(t)$ with unit $\textrm{ps}^{-1}$, while the second
    shows the integrated  probability flux denoted by $Q_{J,I}(t)$.
    A constant $Q_{J,I}$ means vanishing net flux, while a increasing (deceasing)
    $Q_{J,I}$ indicates positive (negative) net flux.
    From left to right, the five
    columns present $I = A_1$, $A_2$, $B_1$, $B_2$ and
    $C$, respectively. In each plot, the red line stands for $J=A_1$,
    green for $J=A_2$, dark blue for $J=B_1$, purple for $J=B_2$ and light blue
    for $J=C$. 
    }
  \label{fig:tmp6}
\end{figure}

% \begin{figure}
%   \centering
%   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-fwd-1.eps}
%   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-fwd-2.eps}
%   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-fwd-3.eps}
%   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-fwd-4.eps}
%   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-fwd-5.eps}\\
%   % \caption{The populations of the metastable sets as a function of time.
%   %   The dashed vertical lines indicate the three different time scale of
%   % metastable set population at $t_{\textrm{warm}} = 10~\textsf{ps}$.}
%   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-bwd-1.eps}
%   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-bwd-2.eps}
%   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-bwd-3.eps}
%   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-bwd-4.eps}
%   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-bwd-5.eps}\\
%   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-flux-1.eps}
%   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-flux-2.eps}
%   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-flux-3.eps}
%   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-flux-4.eps}
%   \includegraphics[width=0.19\textwidth]{fig.ala/fig-trans-100-flux-5.eps}
%   \caption{Forward and backward nonequilibrium transition probability of the case $t_{warm} = 10$~ps.}
%   \label{fig:tmp6}
% \end{figure}

The time-dependent probability of the system in a certain metastable state is given in
Fig.~\ref{fig:tmp5}. The beta sheet conformation $B_1$ and $B_2$,
which presents at the beginning,
fades away as the system relaxes to the new equilibrium. The
probability of alpha helix $A_1$ conformation grows from 0.45 to 0.69.
Alpha helix $A_2$  does not change a lot under the EF.
The left-hand helix conformation $C$ noticeably grows from 0 to 0.22.

We plot the net probability fluxes and their integration in Fig.~\ref{fig:tmp6}.
When $t$ is short, the net fluxes are generally non-zero.
When $t$ goes to infinity,
all fluxes converge to zero. This indicates
when the EF is switched on, the system firstly is driven from the old
equilibrium (in zero EF), and this is a nonequilibrium process.
After a long enough time, the system
is fully relaxed to the new equilibrium defined by the constant EF,
% it gradually relaxes to the new equilibrium,
so we do not see any change
in the population of the metastable states.

\begin{table}
  \centering
  \begin{tabular*}{0.4\textwidth}{@{\extracolsep{\fill}}lc}\hline\hline
    Direction        & time scale [ ps ] \\\hline
    $A_1\rightarrow A_2$        &       $\sim 10$      \\
    $B_1\rightarrow B_2$        &       $\sim 10$      \\    
    $B_2\rightarrow A_1,\ A_2,\ C$        &       $\sim 50$      \\    
    $A_2\rightarrow A_1$        &       $\sim 100$      \\
    $B_2\rightarrow B_1$        &       $\sim 100$      \\    
    $B_1\rightarrow A_1,\ C$        &       $\sim 500$      \\    \hline\hline
  \end{tabular*}
  \caption{A list of main probabilty fluxes and the corresponding time scales observed in the constant EF case.}
  \label{tab:tmp1}
\end{table}

Even though the system is finally relaxed to the new equilibrium,
the speed of relaxation of each metastable state is different. 
From Fig.~\ref{fig:tmp6}, we observe mainly
three different timescales of the conformational relaxation, which
are summarized in Tab.~\ref{tab:tmp1}.
(1) From
$t=0$ to approximately 10~\textsf{ps}, a net flux from 
a flux from $A_1$ to $A_2$.
A similar flux is also observed from $B_1$ to $B_2$.
Then, these two fluxes vanish and then turn to the opposite direction
i.e. $A_2$ to $A_1$ and $B_2$ to $B_1$, respectively.
% the population of $A_1$ firstly decreases and then increases to the original value,
% while the population of $A_2$ increases sharply. The plot of the net probability flux shows that 
% there is firstly a fast probability flux (conformational change) from
% $A_1$ to $A_2$, and then follows a probability flux with the same maganitude in the opposite direction, i.e.  from
% $A_2$ to $A_1$.
In the meanwhile, a net flux from all $\beta$-sheet conformations
($B_1$ and $B_2$) into $\alpha$-helix conformations ($A_1$, $A_2$ and
$C$) has been established.
% Also in this time-scale, strong and increasing probability flux from $B_2$ to $B_1$ is observed from Fig.~\ref{fig:tmp6}.
% The population of $B_1$ remains almost unchanged,
% because it  at the same time loses population to $\alpha$-helix conformations.
% Since  $B_2$ conformations not only changes into $B_1$, but also into $\alpha$-helix conformations, we observe a charp
% decrease of $B_2$ population between 10 and 20~ps.
(2), From $t=10$ to
100~\textsf{ps},
The net flux from  conformation $A_2$ to $A_1$ and from $B_2$ to $B_1$
gradually decays to 0. Conformational change from $B_2$ to $A_1$, $A_2$ and $C$
vanishes in about 50~ps.
% The net flux from $B_1$  to $A_1$ and $C$ decay slower and 
% will be discussed later.
At this stage, the probability of $B_2$ decreases to almost 0,
while the probability of $A_2$
converge to a non-vanishing value of approximately 0.06.
% the population of $B_2$ decreases by 0.15, and this
% configuration almost disappears. Interestingly, the population of $A_1$
% increases by the same amount, and the population of $A_2$ goes back to
% the initial value. The populations of $B_1$ and $C$ start increasing
% and decreasing, correspondingly. The speed of these changes are much
% slower than that of $B_2$ and $A_1$.
(3) At the time scale of $
500~\textsf{ps}$, the population of $A_1$, $B_1$ and $C$ converge to
the new equilibrium (system with $E(\infty) = 1~\textsf{V/m}$).
We observed slowing decaying probability flux from $B_1$ 
to $A_1$ and $C$.
The magnitude of the flux from $B_1$ to  $C$ is larger than that from  $B_1$ to  $A_1$.
% It is interesting to see that at nonequilibrium steady state, $A_1$ exchange
% population with $A_2$, and $B_1$ exchange
% population with $B_2$. However, when the $C$ conformation hardly changes
% to any other conformation, as indicated by the almost 1 value of the forward
% transition probability of set $C$. This implies that at the left-handed $\alpha$-helix is
% acutally more stable than  other conformations.
This time-scale is actually 50 times slower than speed, at which
the EF was switched on ($t_{\textrm{warm}} = 10~\textsf{ps}$).

% After aligning to the external EF, the alanine slowly adjust its conformation,
% and the new equilibrium is reached at slower time scales.

% To further test the dynamics of metastable population, two simulations
% of $t_{\textrm{warm}} = 100~\textsf{ps}$ and $t_{\textrm{warm}} =
% 500~\textsf{ps}$ are performed. The first time scale of $t =
% 20~\textsf{ps}$ disappears in both of the testing simulations. In the
% simulation of $t_{\textrm{warm}} = 100~\textsf{ps}$, the population of
% $A$, $B_1$ and $C$ converges to the non-equilibrium steady state at
% around $500~\textsf{ps}$. This further verifies internal time scale of
% $A_1$, $B_1$ and $C$ presented in the testing case of
% $t_{\textrm{warm}} = 10~\textsf{ps}$.  The dynamics of $B_2$ is
% faster: it decays to zero as soon as the external EF is fully
% switched on. In the case of $t_{\textrm{warm}} = 500~\textsf{ps}$, the
% growth of the external EF is comparable to the longest
% internal time scale of system, which means that the changes of the
% perturbation to the system is so slow that the system can catch up, so
% the process can be treated as  quasi-equilibrium.
% The numerical results show the same story: the relaxation
% of all populations are around $500 \sim 600~\textsf{ps}$.
